Data Preparation, Integration and Cleaning

### 2017-02-08 abbDataPrep_Script.Rmd
Finalize Cancel Policy clean

  ss60 <- which(str.data$cancel.policy == 'Super Strict 60 Days')
  str.data$cancel.policy[ss60] <- 'Strict'
  cpmiss <- which(str.data.ic$cancel.policy == '')
  str.data <- str.data[-cpmiss, ]

>>>>

 ## ID those with missing cancel policies and remove

  cpmiss <- which(str.data$cancel.policy == '')
  str.data <- str.data[-cpmiss, ]

 ## ID those with Super Strict and change to Strict

  ss60 <- which(str.data$cancel.policy == 'Super Strict 60 Days')
  str.data$cancel.policy[ss60] <- 'Strict'
